The Astropy Project

### 2017-11-03 main.tex
Update on Overleaf.

\inlinecomment{David S.}

The \package{Constants} package provides useful physical constants as quantities.  The package was described in \cite{astropy}.  \package{Constants} now include their own version to track when their values are adjusted.

>>>>

%David S.

The \package{Constants} package provides a selection of physical and astronomical
constants as quantities.  A brief description was given in \cite{astropy}. 
For version 2.0, constants have been organized into modules for specific versions.
Physical constants include CODATA2014 and CODATA2010 versions. Astronomical constants
are organized into IAU2015 and IAU2012 versions to roughly indicate their sources.
The CODATA2014 and IAU2015 versions are combined into the default ASTROPYCONST20
version. For astropy v1.3 and earlier, the ASTROPYCONST13 namespace is available;
however when using previous versions of the constants, \package{Constants} should be used
directly; \package{astropy.units} will be initialized to the ASTROPYCONST20 versions.

Astronomers using \package{Constants} should take particular note of the constants
provided for Earth, Jupiter and the Sun. Following IAU 2015 Resolution B3, nominal
values are now given for masses and radii. The nominal values will not change as
estimates of these proper
